---
title: "My first Awesome Project (MAP-1)"
subtitle: "Experiment"
author: "Heinrich Paessens -- paessens|macro.finance"
abstract: > 
  This document is for ...documentation of requirements, implementation and testing. The application is a simple demonstration of End-User-Computing, or Prototyping for that purpose, with a certain software stack and certain specified cornerstones in software development which provides compliance with regulatory minimum requirements and provisions or guidelines (like DORA). 
date: '2026-03-15'
date-modified: "`r Sys.Date()`"
lang: en
format: 
  html:
    fontsize: 13pt
    page-layout: article
    code-summary: "Show the code"
    code-fold: true
    code-link: true
    code-copy: true
    code-overflow: scroll
    code-line-numbers: false
    code-block-bg: true
    code-block-border-left: "#31BAE9"
    code-annotations: false
    code-tools: 
      source: false
      toggle: true
      caption: none
    grid: 
      margin-width: 350px
    html-math-method: katex
    embed-resources: true
    smooth-scroll: true
lightbox: true
fig-format: 'svg'
fig-width: 24
fig-height: 15
fig-show: hold
fig.align: center
tbl.align: center
cap-location: margin
fig-cap-location: margin
tbl-cap-location: margin
reference-location: margin
citation-location: document
anchor-sections: true
number-sections: true
number-depth: 3
toc: true
toc-location: left
toc-depth: 3
number-offset: [3,3,3]
editor: visual
execute:
  cache: true
  include: true
  eval: true
  echo: true
  error: true
  warning: false
knitr:
  opts_chunk: 
    cache: true
    message: false
    warning: false
    error: true
bibliography: lit/ref.bib
bibliographystyle: apa
citations-hover: true
crossrefs-hover: true
author-meta: 'Heinrich Paessens'
copyright: 'Heinrich Paessens (c)2026'
---

## Introduction

### Purpose

### Target Audience

### Use Cases[^1]

[^1]: A use case is a structured description of a system’s behaviour as it responds to requests from external actors, aiming to achieve a specific goal. Specification follows personas in scenarios and maybe visual modelling is supportive here. The context is to focus on usage-centered and activity-centered design, in particular regarding user-interfaces, eventually to get user acceptance.

## Requirements

### Functional Req.[^2]

[^2]: [Functional requirements](https://en.wikipedia.org/wiki/Functional_requirement) (FRs) define what a software system must do, specifying it's behaviors, actions, and features, such as user authentication, data processing, and report generation. It defines *what* the system does (features, behavior).

### Non-Functional Req.[^3]

[^3]: [Non-functional requirements](https://en.wikipedia.org/wiki/Non-functional_requirement)(NFRs) define system attributes such as security, reliability, performance, and usability, specifying "how well" a system performs rather than "what" it does. They act as constraints on the design or implementation, often referred to as '-ilities' (e.g., scalability, maintainability). It's reagarding system quality as well as it considers legal compliance. Sometimes conflicting requirements need choices on trade off and cinsidering technological options available.

## Design

### Data Management

### Business Logic (Rules & Functions)

### User Interface (Presentation Layer)

### Security

### APIs

## Quality Assurance (QA)

### QA by design

### Policies & Procedures

### Technical Tests

### User Acceptance Tests

### Approvals (by role)

## Develop & Implement[^4]

[^4]: Here we do ["Literate Programming"](Literate%20programming), hence integrate source code, execution and presentation. Algorithms are described by readable and comprehensible real code (interpreted) not "pseudo code". The final product might have a different structure, considering optimised compile code and compiler needs & requirements.

### Prototyping

download and read a table of FX fixings from ECB (website)

```{r}
fx <- fread('https://www.ecb.europa.eu/stats/eurofxref/eurofxref-hist.zip')
```

read a spreadsheet for complenting data

```{r}
evt <- read_xlsx('data/events2.xlsx',detect_dates=TRUE)|>setDT(key='date')
```

convert data into time-series-objects, subset (filter) and plot together

```{r}
events <- xts(evt$event,evt$date)['2000::2026-02']
USD.EUR <- fx[Date > '1999-12-31', .(Date,USD)]|>as.xts.data.table()
USD.EUR|>plot(grid.ticks.lty="dotted",lwd=1,col='navy',log=FALSE,ylim=c(.8,1.7))
addEventLines(events,col="#FF5733",lty=1.5,lwd=1.5, srt=90, pos=2,offset=.3,on=0)
```

write data to spreadsheet -- but that roundtrip is trivial

```{r}
usd <- fx[Date > '1999-12-31', .(Date,USD)]
usd|>write_xlsx('testing.xlsx',as_table=TRUE)
```

### Testing

### Final Stage Product

## Operations & Production

### Deployment

### Maintenance
